---
title: "Foil task_Markdown"
author: "Christoph Voelter"
date: "December 09, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
source("Roger_functions/diagnostic_fcns.r")
source("Roger_functions/glmm_stability.r")
source("Roger_functions/boot_glmm.r")
#load(file ="mm1_mult_poss.RData")
#readRDS(file ="multpos_model.rds")
```

```{r loading data, include = FALSE}
Foil.data <- read.table(file="data/20181210foil task_chimps sweetwaters.txt", header=T, sep="\t") %>%
  filter(Phase == "pretest")

```


*** 

##Test against chance 

####Pretest

```{r echo=FALSE}
foil_individual <- Foil.data %>%
  group_by(Subject) %>% 
  summarize(foil.correct = mean(correct)) %>%
  add_count(foil.correct)


tt<-t.test(foil_individual$foil.correct , mu=0.5, alternative = "two.sided")

```
* Mean correct vs chance value (0.5) in **Pretest phase**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`  

```{r echo=FALSE}
knitr::knit_exit()
```




##stop here

#GLMMs with age group as factor

##Summary


###Preprocessing of the data  

```{R include=FALSE}

all.data$Age.cat=relevel(all.data$Age.cat, ref="three")
summary(all.data)

```

```{R include=FALSE}
xx.fe.re=fe.re.tab(fe.model="Correct  ~
                  Trial.type*Order2+Trial.number+
                   Age.cat*Order2+Sex",
                   re="(1|Subject.ID)+(1|Box.type)",
                   data=data.frame(all.data))
xx.fe.re$summary
ydata=xx.fe.re$data
```


  + Scale variables: trial number, age, and order of conditions
```{R include=FALSE}
ripmon1$z.trialno=as.vector(scale(ripmon1$trialno))
ripmon1$z.age=as.vector(ripmon1$scale(age))
```

  + Centering of random slope components of categorical predictors (phase, distractor homogeneity, baited dimension)
```{R include=FALSE}
ydata$Trial.type.sticker.c=ydata$Trial.type.sticker-mean(ydata$Trial.type.sticker)

ydata$Age.cat.five.c=ydata$Age.cat.five-mean(ydata$Age.cat.five)
ydata$Age.cat.four.c=ydata$Age.cat.four-mean(ydata$Age.cat.four)
```

```{r}
#coding dummy variables before centering the slopes
ripmon1$trialtype.food<-as.numeric(ripmon1$trialtype==levels(ripmon1$trialtype)[2])
ripmon1$sex.m<-as.numeric(ripmon1$sex==levels(ripmon1$sex)[2])
ripmon1$phase.transfer<-as.numeric(ripmon1$phase==levels(ripmon1$phase)[2])
```



***

```{r  echo=FALSE}

foil_individual <- ripmon1 %>%
  group_by(phase, id) %>% 
  summarize(foil.correct = mean(correct)) %>%
  add_count(foil.correct)

p1 <- ggplot(
  data=foil_individual, aes(x=phase, y=foil.correct, group=phase)) +
  geom_boxplot()+
  ylim(0,1)+
  geom_point(size = foil_individual$n, colour = "purple") +
  labs(x="",y="Mean number of correct choices")+
  theme_few()+
  ggtitle("Phase")+
  geom_hline(yintercept=0.5, linetype="dashed", color = "red")

foil_individual2 <- ripmon1 %>%
  group_by(trialtype, id) %>% 
  summarize(foil.correct = mean(correct)) %>%
  add_count(foil.correct)

p2 <- ggplot(
  data=foil_individual2, aes(x=trialtype, y=foil.correct, group=trialtype)) +
  geom_boxplot()+
  ylim(0,1)+
  geom_point(size = foil_individual2$n, colour = "purple") +
#  geom_line(lty=2)+
  labs(x="",y="Mean number of correct choices")+
  theme_few()+
  ggtitle("Trial type")+
  geom_hline(yintercept=0.5, linetype="dashed", color = "red")


grid.arrange(p1, p2, nrow = 1, heights=unit(100, "mm"))

```
  
* Dashed line: chance level  


*** 

##Test against chance 

####Test and transfer phase

```{r echo=FALSE}
tt<-t.test(foil_individual$foil.correct[foil_individual$phase=="test"] , mu=0.5, alternative = "two.sided")

```
* Mean correct vs chance value (0.5) in **Test phase**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`  

```{r echo=FALSE}
tt<-t.test(foil_individual$foil.correct[foil_individual$phase=="transfer"] , mu=0.5, alternative = "two.sided")

```
* Mean correct vs chance value (0.5) in **Transfer phase**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 
