---
title: "Foil task - Capuchins - Markdown"
#author: "Christoph Voelter"
date: "December 09, 2018"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(reshape2)
library(car)
#library(brms)
library(BayesFactor)
source("Roger_functions/diagnostic_fcns.r")
source("Roger_functions/glmm_stability.r")
source("Roger_functions/boot_glmm.r")
#load(file ="mm1_mult_poss.RData")
#readRDS(file ="multpos_model.rds")
```

```{r loading data, include = FALSE}
ripmon1<-read.csv("data/ripped_monkey_test16.csv", header=T)
summary(ripmon1)

```

```{r  echo=FALSE}

foil_individual <- ripmon1 %>%
  group_by(phase, id) %>% 
  summarize(foil.correct = mean(correct)) %>%
  add_count(foil.correct)

p1 <- ggplot(
  data=foil_individual, aes(x=phase, y=foil.correct, group=phase)) +
  geom_boxplot()+
  ylim(0,1)+
  geom_point(size = foil_individual$n, colour = "darkblue", alpha=0.3) +
  labs(x="",y="Mean number of correct choices")+
  theme_few()+
  ggtitle("Phase")+
  geom_hline(yintercept=0.5, linetype="dashed", color = "red")

foil_individual2 <- ripmon1 %>%
  group_by(trialtype, id) %>% 
  summarize(foil.correct = mean(correct)) %>%
  add_count(foil.correct)

p2 <- ggplot(
  data=foil_individual2, aes(x=trialtype, y=foil.correct, group=trialtype)) +
  geom_boxplot()+
  ylim(0,1)+
  geom_point(size = foil_individual2$n, colour = "darkblue", alpha=0.3) +
#  geom_line(lty=2)+
  labs(x="",y="Mean number of correct choices")+
  theme_few()+
  ggtitle("Trial type")+
  geom_hline(yintercept=0.5, linetype="dashed", color = "red")


grid.arrange(p1, p2, nrow = 1, heights=unit(100, "mm"))

```
  
* Dashed line: chance level  


*** 

##Test against chance 

####Test and transfer phase

```{r echo=FALSE}
tt<-t.test(foil_individual$foil.correct[foil_individual$phase=="test"] , mu=0.5, alternative = "two.sided")

```
* Mean correct vs chance value (0.5) in **Test phase**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`  

```{r echo=FALSE}
tt<-t.test(foil_individual$foil.correct[foil_individual$phase=="transfer"] , mu=0.5, alternative = "two.sided")

```
* Mean correct vs chance value (0.5) in **Transfer phase**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 


#####Comparison between test and transfer phase

```{r echo=FALSE}
tt<-t.test(foil_individual$foil.correct[foil_individual$phase=="test"], foil_individual$foil.correct[foil_individual$phase=="transfer"], paired = TRUE, alternative = "two.sided")
```
* Difference between test and transfer phase: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`  

* Bayes Factor for the Null Hypothesis (Difference between test and transfer = 0):

```{r echo=FALSE}
bf <- ttestBF(foil_individual$foil.correct[foil_individual$phase=="test"], foil_individual$foil.correct[foil_individual$phase=="transfer"], paired=TRUE)

1 / bf [1]

```

--> Evidence for no difference between test and transfer performance.  


####Trial type

```{r echo=FALSE}
tt<-t.test(foil_individual2$foil.correct[foil_individual2$trialtype=="stick"] , mu=0.5, alternative = "two.sided")

```
* Mean correct vs chance value (0.5) in **Stick trials**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)`  

```{r echo=FALSE}
tt<-t.test(foil_individual2$foil.correct[foil_individual2$trialtype=="food"] , mu=0.5, alternative = "two.sided")

```
* Mean correct vs chance value (0.5) in **Food trials**: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

#####Comparison between stick and food trials

```{r echo=FALSE}
tt<-t.test(foil_individual2$foil.correct[foil_individual2$trialtype=="food"], foil_individual2$foil.correct[foil_individual2$trialtype=="stick"], paired = TRUE, alternative = "two.sided")
```
* Difference between food and stick trials: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 


##GLMM

###Preprocessing of the data  

  + Relevel trial type reference category: "stick" as reference category
  
```{R include=FALSE}
ripmon1$trialtype<-relevel(ripmon1$trialtype, ref = "stick")

```

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="correct ~ trialtype*phase+trialno+age+sex",
                   re="(1|id)",
                   data=data.frame(ripmon1))
xx.fe.re$summary
```


  + Scale variables: trial number and age
```{R include=FALSE}
ripmon1$z.trialno=as.vector(scale(ripmon1$trialno))
ripmon1$z.age=as.vector(scale(ripmon1$age))
```

  + Centering of random slope components of categorical predictors (trial type and phase)

```{r echo=FALSE}
#coding dummy variables before centering the slopes
ripmon1$trialtype.food<-as.numeric(ripmon1$trialtype==levels(ripmon1$trialtype)[2])
ripmon1$phase.transfer<-as.numeric(ripmon1$phase==levels(ripmon1$phase)[2])

ripmon1$phase.transfer.c=ripmon1$phase.transfer-mean(ripmon1$phase.transfer)
ripmon1$trialtype.food.c=ripmon1$trialtype.food-mean(ripmon1$trialtype.food)

```


***

```{r include=FALSE}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
```

####Full model
```{r}
glmm01_full=glmer(correct ~ trialtype*phase+z.trialno+z.age+sex+
             (1+z.trialno+phase.transfer.c+trialtype.food.c|id)+(1|boxtype),
           data=ripmon1, family=binomial, control=contr)
```

####Null model	 
```{r echo=FALSE}
glmm01_null=glmer(correct ~ 1+
             (1+z.trialno+phase.transfer.c+trialtype.food.c|id)+(1|boxtype),
           data=ripmon1, family=binomial, control=contr)
```

  + Full-null model comparison  
```{r echo=FALSE}	 
round(anova(glmm01_null, glmm01_full, test="Chisq"),3)
```

#####Model output
  + Coefficients
```{r echo=FALSE}
round(summary(glmm01_full)$coefficients, 3)
```


  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r echo=FALSE}
xdrop1=drop1(glmm01_full, test="Chisq",control=contr)
round(xdrop1,3)
```




###Reduced model without interactions
####Full model
```{r}
glmm02_full=glmer(correct ~ trialtype+phase+z.trialno+z.age+sex+
             (1+z.trialno+phase.transfer.c+trialtype.food.c|id)+(1|boxtype),
           data=ripmon1, family=binomial, control=contr)
```

Note: removed the interaction between random slope components due to convergence issues for likelihood ratio tests (drop1).

####Null model	 
```{r echo=FALSE}
glmm02_null=glmer(correct ~ 1+
             (1+z.trialno+phase.transfer.c+trialtype.food.c|id)+(1|boxtype),
           data=ripmon1, family=binomial, control=contr)
```

Full-null model comparison
```{r echo=FALSE}	 
round(anova(glmm02_null, glmm02_full, test="Chisq"),3)
```

#####Model output
  + Coefficients
```{r echo=FALSE}
round(summary(glmm02_full)$coefficients, 3)
```


  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r echo=FALSE}
xdrop1=drop1(glmm02_full, test="Chisq",control=contr)
round(xdrop1,3)
```

#####Plot random effects  
```{r echo=FALSE}
plot_model(glmm02_full, type='re')[[1]] 
```

#####Plot predictors
```{R echo=FALSE}
plot_model(glmm02_full, type="est")
```

#####Check for model stability 
Check for model stability by removing levels of the random effects on by one and visualising the resulting variance of each variable
```{R echo=FALSE, warnings=FALSE}
m.stab=glmm.model.stab(model.res=glmm02_full, contr=contr)
m.stab.plot(m.stab$summary[,-1])
```

#####Check for multicollinearity  

```{R echo=FALSE}
xres=lm(correct ~ trialtype+phase+z.trialno+z.age+sex, data=ripmon1)
round(vif(xres),3)
```
--> no colinearity issues.
