---
title: "Ripped Foil - Children - Analysis"
output:
  pdf_document: default
  pdf_notebook: default
  html_document:
    df_print: paged
  html_notebook: default
---

```{r include=FALSE}
#Source functions and load packages
library(lme4)
library(multcomp)
library(car)
library(sjPlot)
library(rethinking)
source("C:/Users/cjv3/R/R scripts/Roger/diagnostic_fcns.r")
source("C:/Users/cjv3/R/R scripts/Roger/glmm_stability.r")
source("C:/Users/cjv3/R/R scripts/Roger/boxplotteR.r")
source("C:/Users/cjv3/R/R scripts/Roger/boot_glmm.r")
source("C:/Users/cjv3/R/R scripts/Roger/corr_exact.r")
#Load and inspect data file.
setwd("~/R/R data analysis/Zeynep_ripped foil/")
getwd()
all.data=read.table(file="Data_ripped_for R.txt", header=T, sep="\t")
summary(all.data)
#load(".RData")
```


#GLMMs with age group as factor

##Summary


###Preprocessing of the data  

```{R include=FALSE}
#3-y-olds as reference catergory
all.data$Age.cat=relevel(all.data$Age.cat, ref="three")
summary(all.data)

```

```{R include=FALSE}
xx.fe.re=fe.re.tab(fe.model="Correct  ~
                  Trial.type*Order2+Trial.number+
                   Age.cat*Order2+Sex",
                   re="(1|Subject.ID)+(1|Box.type)",
                   data=data.frame(all.data))
xx.fe.re$summary
ydata=xx.fe.re$data
```


  + Scale variables: trial number, age, and order of conditions
```{R include=FALSE}
ydata$z.Trial=as.vector(scale(ydata$Trial.number))
ydata$z.Order=as.vector(scale(ydata$Order2))
```

  + Centering of random slope components of categorical predictors (phase, distractor homogeneity, baited dimension)
```{R include=FALSE}
ydata$Trial.type.sticker.c=ydata$Trial.type.sticker-mean(ydata$Trial.type.sticker)
ydata$Sex.m.c=ydata$Sex.m -mean(ydata$Sex.m )
ydata$Age.cat.five.c=ydata$Age.cat.five-mean(ydata$Age.cat.five)
ydata$Age.cat.four.c=ydata$Age.cat.four-mean(ydata$Age.cat.four)
```
***
### Run Model

####Full model
```{r}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
full=glmer(Correct ~ Trial.type*z.Order+z.Trial+Age.cat*z.Order+Sex+
             (1|Subject.ID)+(1|Box.type)+
             (0+z.Trial+z.Order+Trial.type.sticker.c|Subject.ID),
           #+ (0+z.Trial+z.Order+Sex.m.c+Trial.type.sticker.c|Box.type)+
      #     (0+Age.cat.four.c|Box.type)+(0+Age.cat.five.c|Box.type),
           data=ydata, family=binomial, control=contr)
```


####Null model	 
```{r}	 
null=glmer(Correct  ~ 1+
             (1|Subject.ID)+(1|Box.type)+
             (0+z.Trial+z.Order+Trial.type.sticker.c|Subject.ID),
           data=ydata, family=binomial, control=contr)
```
####Full-null model comparison
```{r echo=FALSE}	 
round(anova(null, full, test="Chisq"),3)
```

```{r}
xdrop1=drop1(full, test="Chisq",control=contr)
round(xdrop1,3)
```



####reduced model without interactions
```{r}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
full2=glmer(Correct ~ Trial.type+z.Order+z.Trial+Age.cat+Sex+
             (1|Subject.ID)+(1|Box.type)+
             (0+z.Trial+z.Order+Trial.type.sticker.c|Subject.ID),
           data=ydata, family=binomial, control=contr)
```


```{r}
xdrop1=drop1(full2, test="Chisq",control=contr)
round(xdrop1,3)
```


####Model output
  + Coefficients
```{r}
round(summary(full2)$coefficients, 2)
```

####Posthoc pairwise comparisons
```{R}
xx=glht(full2, linfct = mcp(Age.cat = c("five-three = 0", "four-three = 0", "five-four =0")))
summary(xx)
```